Sablefish equations

### 2024-08-22 ms/equations.tex
added tables with verbose dimensions

% Release model
\begin{equation}
  \label{eq:model-release}
  N_{\boldsymbol{s}_{0},\boldsymbol{t}_{0},l} \sim 
    \mathrm{Binom} \! \left[ x_{s_{0},t_{0},l} \mathrm{,} \: \nu \right]
\end{equation}

% Movement model
\begin{equation}
  \label{eq:model-movement}
  \boldsymbol{P}_{\mathrm{year}[t]} = \boldsymbol{\Gamma}^{K}_{\mathrm{year}[t]}
\end{equation}

@@

% Model indexes
\begin{table}[ht]
  \centering
  \caption{Movement model indexes}
  \renewcommand\arraystretch{1.2}
  \label{tab:model-indexes}
  \begin{tabular}{l l l l r}
    \toprule
    \textbf{Symbol} & \textbf{Condition} & \textbf{Dimension} & \textbf{Definition} & \textbf{Type} \\
    \toprule
    % Index limits
    $S$ & $= 3$ or $6$ & Scalar & Number of spatial regions & Index limit \\
    $T$ & $\in \mathbb{Z}^{+}$ & Scalar & Number of model time steps & Index limit \\
    $K$ & $= 6$ & Scalar & Number of time steps per year & Index limit \\
    $L$ & $= 1$ or $2$ & Scalar & Number of release size classes & Index limit \\
    \midrule
    % Index variables
    $\boldsymbol{s}$ & $= (s_0, s)$ & Vector & Spatial index vector & Vector index \\
    $\boldsymbol{t}$ & $= (t_0, t)$ & Vector & Temporal index vector & Vector index \\
    $\boldsymbol{s}_0$ & $= (s_0, s_0)$ & Vector & Initial spatial index vector & Vector index \\
    $\boldsymbol{t}_0$ & $= (t_0, t_0)$ & Vector & Initial temporal index vector & Vector index \\
    \midrule
    $s$ & $\in \left[1 \, .. \, S \right]$ & Scalar & Spatial region & Index \\
    $t$ & $\in \left[1 \, .. \, T \right]$ & Scalar & Time step & Index \\
    $s_0$ & $\in \left[1 \, .. \, S \right]$ & Scalar & Initial spatial region & Index \\
    $t_0$ & $\in \left[1 \, .. \, T \! - \! 1 \right]$ & Scalar & Initial model time step & Index \\
    $k$ & $\in \left[1 \, .. \, K \right]$ & Scalar & Time step within year & Index \\
    $l$ & $\in \left[1 \, .. \, L \right]$ & Scalar & Release size class & Index \\
    \bottomrule
  \end{tabular}
\end{table}

@@

% Data
\begin{table}[ht]
  \centering
  \caption{Data}
  \renewcommand\arraystretch{1.2}
  \label{tab:data}
  \begin{tabular}{l l l l r}
    \toprule
    \textbf{Symbol} & \textbf{Condition} & \textbf{Dimension} & \textbf{Definition} & \textbf{Type} \\
    \toprule
    $\bm{R}$ & $\in \mathbb{Z}^{+,0}$ & $[N\!-\!1, L][X]$ & Sablefish tags released (counts) & Stepwise \\
    $\bm{C}$ & $\in \mathbb{Z}^{+,0}$ & $[N\!-\!1, D, L][X, X]$ & Sablefish tags recovered (counts) & Stepwise \\
    \bottomrule
  \end{tabular}
\end{table}

% Model derived quantities
\begin{table}[ht]
  \centering
  \caption{Movement model derived quantities}
  \renewcommand\arraystretch{1.2}
  \label{tab:model-derived}
  \begin{tabular}{l l l l r}
    \toprule
    \textbf{Symbol} & \textbf{Condition} & \textbf{Dimension} & \textbf{Definition} & \textbf{Type} \\
    \toprule
    $\bm{A}$ & $\in \mathbb{R}^{+,0}$ & $[N\!-\!1, D, L][X, X]$ & Sablefish tag abundance (numbers) & Stepwise \\
    $\boldsymbol{\widehat{C}}$ & $\in \mathbb{R}^{+,0}$ & $[N\!-\!1, D, L][X, X]$ & Sablefish expected tags recovered (numbers) & Stepwise \\
    $\boldsymbol{\Gamma}$ & $\in \left[0, 1 \right]$ & $[N, L][X, X]$ & Sablefish transition rates & Stepwise \\
    $\bm{S}$ & $\in \left[0, 1 \right]$ & $[N, L][X, X]$ & Sablefish survival rates & Stepwise \\
    $\bm{B}$ & $\in \left[0, 1 \right]$ & $[N, L][X]$ & Sablefish tag observation rates & Stepwise \\
    \midrule
    $\bm{P}$ & $\in \left[0, 1 \right]$ & $[L][X, X]$ & Sablefish movement rates & Annual \\
    $\bm{F}$ & $\in \mathbb{R}^{+,0}$ & $[T, X]$ & Sablefish instantaneous fishing mortality rates & Annual \\
    $\bm{M}$ & $\in \mathbb{R}^{+,0}$ & $[T, X]$ & Sablefish instantaneous natural mortality rates & Annual \\
%    \midrule
%    $\boldsymbol{\Lambda}$ & $\in \left[0, 1 \right]$ & $[L][X, X]$ & Sablefish movement rate deviations & Stepwise \\    
    \bottomrule
  \end{tabular}
\end{table}

>>>>

% Release model
\begin{equation}
  \label{eq:model-release}
  N_{\boldsymbol{s}_{0},\boldsymbol{t}_{0},l} \sim 
    \mathrm{Binom} \! \left[ x_{\boldsymbol{s}_{0},t_{0},l} \mathrm{,} \: \left( 1 - \nu \right) \right]
\end{equation}

% Movement model
\begin{equation}
  \label{eq:model-movement}
  \boldsymbol{P}_{\mathrm{block}[t],l} = \boldsymbol{\Gamma}^{K}_{\mathrm{block}[t],l}
\end{equation}

@@

% Model indexes
\begin{table}[ht]
  \centering
  \caption{Movement model indexes}
  \renewcommand\arraystretch{1.2}
  \label{tab:model-indexes}
  \begin{tabular}{l l l l r}
    \toprule
    \textbf{Symbol} & \textbf{Value} & \textbf{Dimension} & \textbf{Definition} & \textbf{Type} \\
    \toprule
    % Index limits
    $S$ & $= 3$ or $6$ & Scalar & Number of spatial regions & Limit \\
    $T$ & $\in \mathbb{Z}^{+}$ & Scalar & Number of model time steps & Limit \\
    $K$ & $= 6$ & Scalar & Number of time steps per year & Limit \\
    $L$ & $= 1$ or $2$ & Scalar & Number of release size classes & Limit \\
    \midrule
    % Index variables
    $\boldsymbol{s}$ & $= (s_0, s)$ & $[2]$ & Spatial index vector & Index \\
    $\boldsymbol{t}$ & $= (t_0, t)$ & $[2]$ & Temporal index vector & Index \\
    $\boldsymbol{s}_0$ & $= (s_0, s_0)$ & $[2]$ & Initial spatial index vector & Index \\
    $\boldsymbol{t}_0$ & $= (t_0, t_0)$ & $[2]$ & Initial temporal index vector & Index \\
    \midrule
    $s$ & $\in \left[1 \, .. \, S \right]$ & Scalar & Spatial region & Index \\
    $t$ & $\in \left[1 \, .. \, T \right]$ & Scalar & Time step & Index \\
    $s_0$ & $\in \left[1 \, .. \, S \right]$ & Scalar & Initial spatial region & Index \\
    $t_0$ & $\in \left[1 \, .. \, T \! - \! 1 \right]$ & Scalar & Initial model time step & Index \\
    $k$ & $\in \left[1 \, .. \, K \right]$ & Scalar & Time step within year & Index \\
    $l$ & $\in \left[1 \, .. \, L \right]$ & Scalar & Release size class & Index \\
    \bottomrule
  \end{tabular}
\end{table}

% Data
\begin{table}[ht]
  \centering
  \caption{Data}
  \renewcommand\arraystretch{1.2}
  \label{tab:data}
  \begin{tabular}{l l l l r}
    \toprule
    \textbf{Symbol} & \textbf{Value} & \textbf{Dimension} & \textbf{Definition} & \textbf{Type} \\
    \toprule
    $\boldsymbol{y}_{\boldsymbol{t},l}$ & $\in \mathbb{Z}^{+,0}$ & $[S,S][T\!-\!1,T,L]$ & Sablefish tags recovered & Count \\
    $\boldsymbol{x}_{t_0,l}$ & $\in \mathbb{Z}^{+,0}$ & $[S,S][T\!-\!1,L]$ & Sablefish tags released & Count \\
    $\boldsymbol{F}^{\mathrm{assess}}_{\mathrm{year}}$ & $\in \mathbb{R}^{+,0}$ & $[S,S][\mathrm{years}]$ & Annual sablefish fishing mortality & Inst. \\    
    \bottomrule
  \end{tabular}
\end{table}

% Model derived quantities
\begin{table}[ht]
  \centering
  \caption{Movement model derived quantities}
  \renewcommand\arraystretch{1.2}
  \label{tab:model-derived}
  \begin{tabular}{l l l l r}
    \toprule
    \textbf{Symbol} & \textbf{Value} & \textbf{Dimension} & \textbf{Definition}  & \textbf{Type} \\
    \toprule
    $\boldsymbol{N}_{\boldsymbol{t},l}$ & $\in \mathbb{R}^{+,0}$ & $[S,S][T\!-\!1,T,L]$ & Sablefish tag abundance & Numbers \\
    $\boldsymbol{\mu}_{\boldsymbol{t},l}$ & $\in \mathbb{R}^{+,0}$ & $[S,S][T\!-\!1,T,L]$ & Expected tags recovered & Numbers \\
    $\boldsymbol{\Psi}_{t,l}$ & $\in \left[0, 1 \right]$ & $[S,S][T,L]$ & Sablefish tag recovery rate & Stepwise \\
    $\boldsymbol{\Lambda}_{t,l}$ & $\in \left[0, 1 \right]$ & $[S,S][T,L]$ & Sablefish tag survival rate & Stepwise \\    
    $\boldsymbol{P}_{\mathrm{block},l}$ & $\in \left[0, 1 \right]$ & $[S,S][\mathrm{blocks},L]$ & Sablefish movement rate & Yearly \\
    \bottomrule
  \end{tabular}
\end{table}

% Model parameters
\begin{table}[ht]
  \centering
  \caption{Movement model parameters}
  \renewcommand\arraystretch{1.2}
  \label{tab:model-parameters}
  \begin{tabular}{l l l l r}
    \toprule
    \textbf{Symbol} & \textbf{Value} & \textbf{Dimension} & \textbf{Definition} & \textbf{Type} \\
    \toprule
    $\boldsymbol{\Gamma}_{\mathrm{block},l}$ & $\in \left[0, 1 \right]$ & $[S,S][\mathrm{blocks},L]$ & Sablefish movement rate & Stepwise \\
    $\boldsymbol{\omega}_{k}$ &  $\in \left[0, 1 \right]$ & $[S,S][K]$ & Seasonal fishing mortality weight & Stepwise \\
    \midrule
    $\boldsymbol{F}_{\mathrm{year}}$ & $\in \mathbb{R}^{+,0}$ & $[S,S][\mathrm{years}]$ & Annual sablefish fishing mortality rate & Inst. \\
    $\boldsymbol{M}$ & $\in \mathbb{R}^{+,0}$ & $[S,S]$ & Annual sablefish natural mortality rate & Inst. \\
    $\eta$ & $\in \mathbb{R}^{+,0}$ & Scalar & Annual sablefish tag loss rate & Inst. \\    
    \midrule
    $\boldsymbol{\lambda}_{l}$ & $\in \left[0, 1 \right]$ & $[S,S][L]$ & Sablefish fisheries size selectivity & Per fish \\
    $\boldsymbol{W}$ & $\in \left[0, 1 \right]$ & $[S,S]$ & Sablefish tag reporting rate & Per tag \\
    $\nu$ & $\in \left[0, 1 \right]$ & Scalar & Sablefish initial tag loss rate & Per tag \\
    \midrule
    $\phi$ & $\in \mathbb{R}^{+}$ & Scalar & Negative binomial dispersion & NB2 \\
%    \midrule
    \bottomrule
  \end{tabular}
\end{table}

@@

% Data
\begin{table}[ht]
  \centering
  \caption{Data}
  \renewcommand\arraystretch{1.2}
  \label{tab:data-0}
  \begin{tabular}{l l l l r}
    \toprule
    \textbf{Symbol} & \textbf{Condition} & \textbf{Dimension} & \textbf{Definition} & \textbf{Type} \\
    \toprule
    $\bm{R}$ & $\in \mathbb{Z}^{+,0}$ & $[N\!-\!1, L][X]$ & Sablefish tags released (counts) & Stepwise \\
    $\bm{C}$ & $\in \mathbb{Z}^{+,0}$ & $[N\!-\!1, D, L][X, X]$ & Sablefish tags recovered (counts) & Stepwise \\
    \bottomrule
  \end{tabular}
\end{table}

% Model derived quantities
\begin{table}[ht]
  \centering
  \caption{Movement model derived quantities}
  \renewcommand\arraystretch{1.2}
  \label{tab:model-derived-0}
  \begin{tabular}{l l l l r}
    \toprule
    \textbf{Symbol} & \textbf{Condition} & \textbf{Dimension} & \textbf{Definition} & \textbf{Type} \\
    \toprule
    $\bm{A}$ & $\in \mathbb{R}^{+,0}$ & $[N\!-\!1, D, L][X, X]$ & Sablefish tag abundance (numbers) & Stepwise \\
    $\boldsymbol{\widehat{C}}$ & $\in \mathbb{R}^{+,0}$ & $[N\!-\!1, D, L][X, X]$ & Sablefish expected tags recovered (numbers) & Stepwise \\
    $\boldsymbol{\Gamma}$ & $\in \left[0, 1 \right]$ & $[N, L][X, X]$ & Sablefish transition rates & Stepwise \\
    $\bm{S}$ & $\in \left[0, 1 \right]$ & $[N, L][X, X]$ & Sablefish survival rates & Stepwise \\
    $\bm{B}$ & $\in \left[0, 1 \right]$ & $[N, L][X]$ & Sablefish tag observation rates & Stepwise \\
    \midrule
    $\bm{P}$ & $\in \left[0, 1 \right]$ & $[L][X, X]$ & Sablefish movement rates & Annual \\
    $\bm{F}$ & $\in \mathbb{R}^{+,0}$ & $[T, X]$ & Sablefish instantaneous fishing mortality rates & Annual \\
    $\bm{M}$ & $\in \mathbb{R}^{+,0}$ & $[T, X]$ & Sablefish instantaneous natural mortality rates & Annual \\
%    \midrule
%    $\boldsymbol{\Lambda}$ & $\in \left[0, 1 \right]$ & $[L][X, X]$ & Sablefish movement rate deviations & Stepwise \\    
    \bottomrule
  \end{tabular}
\end{table}
